Structure Learning for $\VAR(p)$ Models

### 2019-03-18 paper.tex
Some symbolic algebra, not important.

\newcommand{\linE}[2]{\hat{\E}[#1\ |\ #2]}  % Linear projection
\newcommand{\linEerr}[2]{\xi[#1\ |\ #2]}  % Error of linear projection
\newcommand{\pa}[1]{pa(#1)}  % Parents of a node
\newcommand{\anc}[1]{\mathcal{A}(#1)}  % Ancestors of a node
\newcommand{\ancn}[2]{\mathcal{A}_{#1}(#2)}  % nth ancestors of a node
\newcommand{\gpn}[2]{gp_{#1}(#2)}  # nth generation grandparents
\newcommand{\gcgpath}[4]{#1 \rightarrow #2_1 \rightarrow \cdots \rightarrow #2_{#3} \rightarrow #4}

@@

\title{Structure Learning for $VAR(p)$ Models}
\author{R. J. Kinnear, R. R. Mazumdar}

@@

  The base case follows by expanding \ref{eqn:parent_expansion}, but we skip the calculations since they are nearly identical to the following induction step:

@@

  Where set $(a)$ follows by expanding each $x_k$ with equation \ref{eqn:parent_expansion} and $(b)$ requires the inversion of $\big(1 - \sum_{k \in \gpn{\ell}{i}\setminus\{i\}}\wtB_{ik}(z)\wtB_{ki}(z)\big)$ as well as using the fact that $\ancn{\ell}{i} = \ancn{\ell - 1}{i}\cup\gpn{\ell}{i}$.  We here remind the reader of our earlier established convention that $\wtB$ simply represents the existence of a filter (possibly 0) and can change from place to place.

>>>>

\newcommand{\linE}[2]{\hat{\E}[#1\ |\ #2]}  % Linear projection
\newcommand{\linEerr}[2]{\xi[#1\ |\ #2]}  % Error of linear projection
\newcommand{\pa}[1]{pa(#1)}  % Parents of a node
\newcommand{\anc}[1]{\mathcal{A}(#1)}  % Ancestors of a node
\newcommand{\ancn}[2]{\mathcal{A}_{#1}(#2)}  % nth ancestors of a node
\newcommand{\gpn}[2]{gp_{#1}(#2)}  % nth generation grandparents
\newcommand{\gcgpath}[4]{#1 \rightarrow #2_1 \rightarrow \cdots \rightarrow #2_{#3} \rightarrow #4}

@@

\title{Structure Learning for $\VAR(p)$ Models}
\author{R. J. Kinnear, R. R. Mazumdar}

@@

  The base case follows by expanding each $x_k$ in equation \ref{eqn:induction} via equation \ref{eqn:parent_expansion}, but we skip the calculations since they are nearly identical to the following induction step:

@@

  Where equality $(a)$ follows by expanding each $x_k$ with equation \ref{eqn:parent_expansion} and $(b)$ requires the inversion of $\big(1 - \sum_{k \in \gpn{\ell}{i}\setminus\{i\}}\wtB_{ik}(z)\wtB_{ki}(z)\big)$ as well as using the fact that $\ancn{\ell}{i} = \ancn{\ell - 1}{i}\cup\gpn{\ell}{i}$.  We here remind the reader of our earlier established convention that $\wtB$ simply represents the existence of a filter (possibly 0) and can change from place to place.
